A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2024-11-12 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
Minor typos

\begin{tcolorbox}[colback=white, colframe=black]
	Statistical mixture of ensemble $\Rightarrow$ An ensemble space $\Ens$ is a topological convex space.
\end{tcolorbox}

\subsection{Entropy}
The last requirement is that each ensemble must have a well defined \textbf{entropy}. That is, there is a scalar function $S : \Ens \to \mathbb{R}$ that satisfies the following
\begin{enumerate}
	\item strictly concave: $S(p \ens[a] + (1-p) \ens[b]) - (p S(\ens[a]) + (1-p) S(\ens[b]) ) \geq 0$
	\item bounded from above: $S(p \ens[a] + (1-p) \ens[b]) - (p S(\ens[a]) + (1-p) S(\ens[b]) ) \leq - p \log p - (1-p) \log(1-p)$
\end{enumerate}
The first tells us that, during mixing, the entropy cannot decrease, and it stays the same if and only we are mixing an ensemble with itself. The second tells us that the most the entropy can increase is given by the choice between the two ensembles.\footnote{It can be shown that if an upper bound that only depends on the mixing coefficients exists, then it must be the Shannon entropy.}

>>>>

\begin{tcolorbox}[colback=white, colframe=black]
	Statistical mixture of ensembles $\Rightarrow$ An ensemble space $\Ens$ is a topological convex space.
\end{tcolorbox}

\subsection{Entropy}
The last requirement is that each ensemble must have a well defined \textbf{entropy}. That is, there is a scalar function $S : \Ens \to \mathbb{R}$ that satisfies the following:
\begin{enumerate}
	\item strictly concave: $S(p \ens[a] + (1-p) \ens[b]) - (p S(\ens[a]) + (1-p) S(\ens[b]) ) \geq 0$
	\item bounded from above: $S(p \ens[a] + (1-p) \ens[b]) - (p S(\ens[a]) + (1-p) S(\ens[b]) ) \leq - p \log p - (1-p) \log(1-p)$
\end{enumerate}
The first tells us that, during mixing, the entropy cannot decrease, and it stays the same if and only we are mixing an ensemble with itself. The second tells us that the most the entropy can increase is given by the choice between the two ensembles.\footnote{It can be shown that if an upper bound that only depends on the mixing coefficients exists, then it must be the Shannon entropy.}
